\section{Related Work}
What-IF~\cite{Herodotou2011Profiling} is a performance prediction engine, which is applied to the self-tuning system for the MapReduce called Starfish\cite{Herodotos2011}. The authors propose a model to predict respectively the execution time of the map and reduce task, but it doesn't consider the parallelism between multiple phases inside the map or reduce task. Shi~\cite{Shi2014MRTuner} proposes a novel Producer-Transporter-Consumer(PTC) model, which is adopted by the MRTuner to optimize the configuration parameters of MapReduce jobs. The model address the issues of inter-task parallelization, and this issue occurs when there are reduce and map tasks simultaneously executing. At this moment, the shuffle phase of the reduce task is in parallel with the map task, our MR. Prophet also holds the ability to predict the effective time of this reduce task's shuffle phase, but the PTC can't capture the multiple phases' overlap time.

There are other researches to predict the MapReduce job's execution time. MRPerf~\cite{Wang2009A} is the existing simulators which predict the execution time of MapReduce job through the simulation. MRPerf provides the fine-grained simulation of the MapReduce job at sub-phase level like our MR. Prophet. However, the MRPerf has to take a relatively long time to predict the MapReduce job's cost due to the use of external network simulator to predict the cost of data transfers. MRShare~\cite{Nykiel2010MRShare} is a framework to transform a batch of queries into a new batch that will be executed more efficiently, the authors proposes a cost model for this optimization, but this cost model is so simplified and it just considers the total cost of read, sort and write. The related researches\cite{Song2013A}\cite{Lin2012A}\cite{Teng2011SimMapReduce} propose some other approaches to predict the cost of MapReduce jobs, but they don't find the issue of phases parallelism.
